% First, define the Title 
\def\documenttitle{Info Sheet}

% Require the BWOK preamble
\input{bwokpre}

\usepackage{wrapfig}

\begin{document}

% Big BWOK header
\bwokbigheader

% Standard Title and Client Name
\bwoktitle{\documenttitle}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACTUAL CONTENT STARTS HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Site Texts}

Brighton Wok: The Legend of Ganja Boxing

2008

90 mins

http://www.brighton-wok.com

NINJAS - GANJA - KUNG-FU

Ninjas are taking over Brighton. Terrorising locals, killing hippies, blocking supplies of marijuana.
 
Can The Chosen One learn the ancient martial art of Ganja Boxing to save his home town and avenge his past?
 
First, he must find The Ganja Master.
 
The British cult-classic of the 2000’s, Brighton Wok is a micro-budget, independent feature film available on widescreen DVD with 5.1 surround sound.
 
A Stoner Film and a Kung Fu comedy set – incongruously – in an English seaside resort and inspired by comic culture and 80’s movies.
 
Brighton Wok was filmed all over Sussex, with locations including: The Hundred Acre Wood (Winnie the Pooh), Chanctonbury Ring, Devils' Dyke, Seaford, Beachy Head, Ditchling Beacon, Woodingdean, Harrison's Rocks, all over Brighton and of course Hove.

Director: Gabriel Howard

IMDB:  http://www.imdb.com/title/tt1233253/

Selling online and at independent video shops across the world.

Recommended Retail Price: £9.99

Production Company: Convict Films http://convictfilms.com




%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACTUAL CONTENT ENDS HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Require the BWOK footer
\input{bwokpost}

\end{document}
